\bf Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 appendix.tex
Added initial computation for the side length
Added intial triangle
Added the notations
Added the equations with a flow

>>>>

\includegraphics[width=1\textwidth,height=0.3\textheight]{appendix_files/figure-pdf/fig-tri-param-1.pdf}

\caption{\label{fig-tri-param}The components of the right triangle
illustrating notation.}

By applying the Pythagorean theorem, we obtain,

\[
l^2 = \left(\frac{a_1}{2}\right)^2 + \left(\frac{a_2 - l}{2}\right)^2.
\] Next, rearranging the terms, we get,

\[
l^2 - \left(\frac{a_2 - l}{2}\right)^2 = \left(\frac{a_1}{2}\right)^2,
\]

\[
\left[l - \left(\frac{a_2 - l}{2}\right)\right]\left[l + \left(\frac{a_2 - l}{2}\right)\right] = \left(\frac{a_1}{2}\right)^2,
\]

\[
3l^2 + 2a_2l - (a_1^2 + a_2^2) = 0.
\]

Finally, by solving the quadratic equation, we compute,

\[
l = \frac{-2a_2 \pm \sqrt{4a_2^2 - 24[-(a_1^2 + a_2^2)]}}{6},
\]

\[
l = \frac{-a_2 \pm \sqrt{a_2^2 - 6[-(a_1^2 + a_2^2)]}}{3},
\]

where \(l > 0\).
